Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-30 paper.qmd

gau1_model <- fit_highd_model(
  training_data = training_data_gau,
  emb_df = tsne_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1,
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = FALSE,
  col_start_highd = "x",
  q = 0.1
)

@@

gau1_model <- fit_highd_model(
  training_data = training_data_gau,
  emb_df = umap_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1,
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = FALSE,
  col_start_highd = "x"
)

@@

gau1_model <- fit_highd_model(
  training_data = training_data_gau,
  emb_df = pacmap_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1,
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = FALSE,
  col_start_highd = "x",
  q = 0.1
)

@@

algo_obj_pbmc <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_pbmc, 
  nldr_data = umap_pbmc, 
  num_x_bins = num_bins_x_pbmc,
  col_start = "pc")

@@

algo_obj_mnist <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_mnist, 
  nldr_data = tsne_mnist2, 
  num_x_bins = num_bins_x_mnist,
  col_start = "PC")

>>>>

gau1_model <- fit_highd_model(
  highd_data = training_data_gau,
  nldr_data = tsne_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1,
  is_bin_centroid = TRUE,
  q = 0.1
)

@@

gau1_model <- fit_highd_model(
  highd_data = training_data_gau,
  nldr_data = umap_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1,
  is_bin_centroid = TRUE,
  q = 0.1
)

@@

gau1_model <- fit_highd_model(
  highd_data = training_data_gau,
  nldr_data = pacmap_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1,
  is_bin_centroid = TRUE,
  q = 0.1
)

@@

algo_obj_pbmc <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_pbmc, 
  nldr_data = umap_pbmc, 
  num_x_bins = num_bins_x_pbmc)

@@

algo_obj_mnist <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_mnist, 
  nldr_data = tsne_mnist2, 
  num_x_bins = num_bins_x_mnist)
